Check Coverage

### 2019-11-13 analysis/merge_data.Rmd
modify future_map

Get FD metrics for each study 
```{r}
library(furrr)
load(here::here("data", "biotime_traits.rda"))

get_fd <- function(data, study, plot_num){
  print(max(data$record_id))

@@

@@

get_fd_safe <- possibly(get_fd, NA)

data <- biotime_traits %>% 
  filter(!is.na(plot), !is.na(scientificName)) %>% #remove unlabeled plots and observations without traits
  group_by(study_id, year, plot) %>%
  filter(n_distinct(id) > 4) %>%
  ungroup() %>%
  filter(study_id == 516)

combs <- cross2(unique(data$study_id), unique(data$plot))

plan(multiprocess)
fd <- future_map_dfr(combs, ~ get_fd_safe(data = data, study = .x[1], plot = .x[2]))  
```

Read data back in:
```{r}
# files <-  dir(here::here("data", "fd_output"), "*.tsv")
# 
# fd_data <- files %>%
#   paste0(here::here("data", "fd_output"), "/", .) %>%
#   map_dfr(read_tsv)
# 
# fd <- biotime_traits %>%
#   filter(!is.na(plot), !study_id %in% c(195, 360)) %>%
#   anti_join(fd_data) %>%
#   group_by(study_id, year, plot) %>%
#   filter(n_distinct(id) > 4) %>%
#   ungroup() %>%
#   group_by(study_id, plot) %>%
#   group_map(~get_fd_safe(.x, study = .y$study_id, plot = .y$plot))
# 
# #4610981
# #7611121

```

Format tables
```{r}
fd_table <- fd %>% 
  select(year, study_id, plot, richness = nbsp, everything(), -sing.sp) %>%
  gather(metric, value, contains("F"), RaoQ) %>%
  View()
```

>>>>

Get FD metrics for each study

FD function:
```{r}
library(furrr)
load(here::here("data", "biotime_traits.rda"))

get_fd <- function(data, study, plot_num){
  require(FD)

@@

  print(max(data$record_id))

@@

get_fd_safe <- possibly(get_fd, NA)
```

First pass at calculating FD metrics
```{r}
data <- biotime_traits %>% 
  filter(!is.na(plot), !is.na(scientificName)) %>% #remove unlabeled plots and observations without traits
  group_by(study_id, year, plot) %>%
  filter(n_distinct(id) > 4) %>%
  ungroup() %>%
  filter(!study_id %in% c(195, 360), #exclude because they break
         !study_id %in% c(217, 327)) #exclude to get the file size smaller

combs <- data %>%
  select(study_id, plot) %>%
  distinct()

plan(multiprocess)
system.time(fd <- future_pmap_dfr(combs, ~ get_fd(data = data, study = .x, plot = .y)))
```

Read data back in, excluding sites/plots as they become a problem:
```{r}
files <-  dir(here::here("data", "fd_output"), "*.tsv")

fd_data <- files %>%
  paste0(here::here("data", "fd_output"), "/", .) %>%
  map_dfr(read_tsv)

remain <- biotime_traits %>%
  filter(!is.na(plot), !is.na(scientificName)) %>% #remove unlabeled plots and observations without traits
  filter(!is.na(plot), !study_id %in% c(195, 360),
         !study_id %in% c(217, 327), #exclude to get the file size smaller
         !study_id %in% c(59, 166, 337), #NA's in the distance matrix
         study_id != 169,  #Zero distance error
         !study_id %in% c(372,374), #Qhull error code 4
         study_id != 333) %>% #species distance matrix not Euclidean after 'sqrt' correction
  filter(study_id != 56 | plot != 24) %>% #NA's in the distance matrix
  anti_join(fd_data, by = c("year", "study_id", "plot")) %>%
  group_by(study_id, year, plot) %>%
  filter(n_distinct(id) > 4) %>%
  ungroup()

combs <- remain %>%
  select(study_id, plot) %>%
  distinct()

plan(multiprocess)
system.time(fd <- future_pmap_dfr(combs, ~ get_fd(data = remain, study = .x, plot = .y)))
```

Format tables
```{r}
fd_table <- fd_data %>% 
  select(year, study_id, plot, richness = nbsp, everything(), -sing.sp) %>%
  gather(metric, value, contains("F"), RaoQ)

usethis::use_data(fd_table)
```
